Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-16 WSSSPE3/report/wg_main_industry_interaction.tex
Section 5.3: Added a question and request for review.
small edits to edits and other in 5.3

Can we determine what each partner wants to get out of such a collaboration?
Why would industry be interested in collaborating with academia? 
Why would academia be interested in collaborating with industry?

@@

Complete a set of case studies which look at successful and unsuccessful
transitions of researchers between academia and industry. This might address 
each of the transition types (described below). Successful transitions are
described as those that lead to either weak or strong sustainability (also
defined below).

@@

\item Sponsorship Model: academia writes and maintains the software; the
industry contributes funding for the development\slash maintenance of software.
In this example, industry is also likely a user of the software.

\item Spinoff model: transition to for- or non-profit company owned by or in
collaboration with original developers.

@@

\end{itemize}
We refer readers to Becker et al.~\cite{Becker:2014} for extended discussion of weak versus strong
sustainability. For more detail on the group's discussion, see
Appendix~\ref{sec:appendix_industry_interaction}.

>>>>

Can we determine what each partner wants to get out of such a collaboration?
For example, why would industry be interested in collaborating with academia? 
Or why would academia be interested in collaborating with industry?

@@

A set of case studies that look at successful and unsuccessful
transitions of researchers between academia and industry. This might address 
each of the transition types (described below). Successful transitions are
described as those that lead to either weak or strong sustainability (also
defined below).

@@

\item Sponsorship Model: academia writes and maintains the software; 
industry contributes funding for the development\slash maintenance of software.
In this example, industry is also likely a user of the software.

\item Spinoff model: transition to a for-profit or non-profit company owned by or in
collaboration with original developers.

@@

\end{itemize}
We refer readers to Becker et al.~\cite{Becker:2014} for an extended discussion of weak versus strong
sustainability. For more detail on the group's discussion, see
Appendix~\ref{sec:appendix_industry_interaction}.
